Formatting a Master's Thesis and a bunch of other things that are not really needed in here

### 2020-09-18 MScTemplateCS.tex
Fixed uneven line spacing in the title on the cover.
Changed Bibliography name to References - this can be easily done in the document now.
Added Swedish title request, magic number for LU-CS-EX

%\documentclass[nofilelist]{cslthse-msc}
% to show a list of used packages at the end of the document, delete the nofilelist option
\documentclass{cslthse-msc} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
%\usepackage{amsfonts}
%%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}

@@

\thesisnumber{LU-CS-EX: 2019-XX} % Birger Swahn will provide this number to you, once the thesis is ready for publication
% default is Master. Uncomment the following for "kandidatarbete"/Bachelor's thesis
%\thesistype{Bachelor}{Kandidatarbete}

%\title{Formatting a Master's Thesis}
\title{Formatting a Master's Thesis and a bunch of other things that are not really needed in here}

@@

We would also like thank Camilla Lekebjer for her contribution on this template, as well as Magnus Hultin for his popular science summary class and example document.
}

@@

\begin{document}
\makefrontmatter
\chapter[Short on Formatting]{Formatting}
Avoid empty spaces between \textit{chapter}-\textit{section}, \textit{section}-\textit{sub-section}. For instance, a very brief summary of the chapter would be one way of bridging the chapter heading and the first section of that chapter.
\section{Page Size and Margins}
Use A4 paper, with the text margins given in Table \ref{tab:margins}.
\begin{table}[!hbt]
\centering
\caption{Text margins for A4.}\label{tab:margins}
\begin{tabular}{cc}
\hline
\textbf{margin} & \textbf{space} \\
\hline 
top &  3.0cm\\

@@

\end{description}
% Should use consistent formatting when it comes to Names ("FirstName LastName", or "F. LastName")
\makebibliography{MyMSc}

@@

>>>>

\documentclass[nofilelist]{cslthse-msc}
% to show a list of used packages at the end of the document, delete the nofilelist option
%\documentclass{cslthse-msc} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
%\usepackage{amsfonts}
%%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}

@@

\thesisnumber{LU-CS-EX: 2023-79} % Magic Number! Do not change unless Birger Swahn asks you to do so!
% default is Master. Uncomment the following for "kandidatarbete"/Bachelor's thesis
%\thesistype{Bachelor}{Kandidatarbete}

%\title{Formatting a Master's Thesis}
\title{Formatting a Master's Thesis and a bunch of other things that are not really needed in here}
\svensktitel{Infoga den Svenska titel här!}

@@

We would also like thank Camilla Lekebjer for her contribution on this template, as well as Magnus Hultin for his popular science summary class and example document.

Thanks also go to the following (former) students for helping with feedback and suggestions on this template: Mikael Persson, Christoffer Lundgren, Mahmoud Nasser.
}

@@

\begin{document}
\renewcommand{\bibname}{References}

\makefrontmatter
\chapter[Short on Formatting]{Formatting}
Avoid empty spaces between \textit{chapter}-\textit{section}, \textit{section}-\textit{sub-section}. For instance, a very brief summary of the chapter would be one way of bridging the chapter heading and the first section of that chapter.
\section{Page Size and Margins}
Use A4 paper, with the text margins given in Table \ref{tab:margins}.
\begin{table}[!hbt]
\centering
\caption{Text margins for A4.}\label{tab:margins}
\begin{tabular}{cc}
\hline
\textbf{margin} & \textbf{space} \\
\hline 
top &  3.0cm\\

@@

\end{description}
% Should use consistent formatting when it comes to Names ("FirstName LastName", or "F. LastName")
%\printbibliography
\makebibliography{MyMSc}

@@

\subsubsection{Since 2020/09/18}
\begin{itemize}
\item Added the Swedish title displayed on page 3. Use \verb+\svensktitel{...}+ command to set it.
\item Converted the default LU-CS-EX number to a magic number, \verb+2023-79+, easy to find and change in PDF with \verb+changepagestring.pl+; this is a \verb+perl+ command line utility found in \verb+CAM::PDF+ module -- but only works on some PDFs (e.g. generated with \verb+pdflatex+) but not others (e.g. \verb+xelatex+) \textbf{[CS internal use]}
\end{itemize}

\subsubsection{Since 2019/10/30}
\begin{itemize}
\item Bibliography is now called References. This can be easily adjusted by changing \\ \verb+\renewcommand{\bibname}{References}+ after \verb+\begin{document}+.
\end{itemize}
